Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
nudge

While program termination has been extensively studied, much less research
has been conducted in the area of proving non-termination.  Gupta et
al.~dynamically enumerate lasso-shaped candidate paths for counterexamples,
and then statically prove their
feasibility~\cite{DBLP:conf/popl/GuptaHMRX08}.  Chen et al.~prove
nontermination via reduction to safety
proving~\cite{DBLP:conf/tacas/ChenCFNO14}.  Their iterative algorithm uses
counterexamples to a fixed safety property to refine an under-approximation
of a program.  In order to prove both termination and non-termination,
Harris et al.~compose several program analyses (termination provers for
multi-path loops, non-termination provers for cycles, and global safety
provers)~\cite{DBLP:conf/sas/HarrisLNR10}.  We propose a uniform treatment
of termination and non-termination by formulating a generalised second order
formula whose solution is a proof of one of them.

>>>>

While program termination has been extensively studied, much less research
has been conducted in the area of proving non-termination.  Gupta et
al.~dynamically enumerate lasso-shaped candidate paths for counterexamples,
and then statically prove their
feasibility~\cite{DBLP:conf/popl/GuptaHMRX08}.  Chen et al.~prove
nontermination via reduction to safety
proving~\cite{DBLP:conf/tacas/ChenCFNO14}.  Their iterative algorithm uses
counterexamples to a fixed safety property to refine an under-approximation
of a program.  In order to prove both termination and non-termination,
Harris et al.~compose several program analyses (termination provers for
multi-path loops, non-termination provers for cycles, and global safety
provers)~\cite{DBLP:conf/sas/HarrisLNR10}.  We propose a uniform treatment
of termination and non-termination by formulating a generalised second-order
formula whose solution is a proof of one of them.
